\documentclass[]{article}

%% Added By Lucktroy
\usepackage{booktabs}
\usepackage{mdwlist}
\renewenvironment{description}{
  \begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{10em}}
}{
  \end{basedescript}
}
%%

\usepackage{geometry} 		% 設定邊界
\geometry{
  top=1in,
  inner=1in,
  outer=1in,
  bottom=1in,
  headheight=3ex,
  headsep=2ex
}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec} 	% 允許設定字體
  \usepackage{xeCJK} 		% 分開設置中英文字型
  \setCJKmainfont{LiHei Pro} 	% 設定中文字型
  \setmainfont{Georgia} 	% 設定英文字型
  \setromanfont{Georgia} 	% 字型
  \setmonofont{Courier New}
  \linespread{1.2}\selectfont 	% 行距
  \XeTeXlinebreaklocale "zh" 	% 針對中文自動換行
  \XeTeXlinebreakskip = 0pt plus 1pt % 字與字之間加入0pt至1pt的間距，確保左右對整齊
  \parindent 0em 		% 段落縮進
  \setlength{\parskip}{20pt} 	% 段落之間的距離
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines

\title{\huge 在OSX平台上的XeLaTeX中文測試} % 設置標題，使用巨大字體
\author{FoolEgg.com} 		% 設置作者
\date{February 2013} 		% 設置日期
\usepackage{titling}
\setlength{\droptitle}{-8em} 	% 將標題移動至頁面的上面

\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

\setcounter{secnumdepth}{0}

\author{}
\date{}

\begin{document}

\section{Junbo Zhang}\label{junbo-zhang}

\input{0-contact}

\iffalse
School of Information Science and Technology :
\href{mailto:jbzhang@my.swjtu.edu.cn}{jbzhang@my.swjtu.edu.cn}

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[Southwest Jiaotong University, Chengdu, China]
\url{http://www.lucktroy.org}
\end{description}

\subsection{Short Bio}\label{short-bio}

Junbo Zhang is currently a Research Assistant at The Chinese University
of Hong Kong and a Research Intern at Huawei Noah's Ark Lab (Hong Kong).
He received his B.Eng. degree in Telecommunication Engineering (the Mao
Yisheng Honors Class) from Southwest Jiaotong University. He was a
visiting Ph.D.~student at the Department of Computer Science, Georgia
State University (Feb. 2012 - Feb. 2013) and an Intern at the Belgian
Nuclear Research Centre (SCK-CEN), Belgium (Aug. 2011 - Sep. 2011). He
is a student member of both ACM and China Computer Federation. \fi

\subsection{Education}\label{education}

\begin{description}
\item[9/2009 - present]
PhD Candidate in School of Information Science and Technology

Southwest Jiaotong University
\item[9/2005 - 7/2009]
BEng in Telecommunication Engineering from Southwest Jiaotong University
\end{description}

\subsection{Experience}\label{experience}

\begin{description}
\item[5/2013 - present]
Research Assistant at The Chinese University of Hong Kong, Hong Kong
\item[5/2013 - present]
Research Intern at \href{http://www.noahlab.com.hk/}{Huawei Noah's Ark
Lab (Hong Kong)}, Hong Kong
\item[2/2012 - 2/2013]
Visiting PhD Student at Georgia State University, USA
\item[8/2011 - 9/2011]
Intern at Belgian Nuclear Research Centre (SCK-CEN), Belgium
\end{description}

\subsection{Research Topics}\label{research-topics}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Deep Learning, Representation Learning, Feature Selection
\item
  Cloud Computing, Distributed Computing, High Performance Computing
\item
  Big Data Mining
\item
  Rough Sets/Fuzzy Sets
\end{itemize}

\subsection{Publications}\label{publications}

\begin{itemize}
\item
  \textbf{Junbo Zhang}, Guangjian Tian, Yadong Mu, Wei Fan.\\
  \emph{Supervised Deep Learning with Auxiliary Networks.}\\ The 20th
  ACM SIGKDD Conference on Knowledge Discovery and Data Mining
  (\href{http://www.kdd.org/kdd2014/}{\textbf{KDD 2014}}).
\item
  \textbf{Junbo Zhang}, Jian-Syuan Wong, Yi Pan, Tianrui Li.\\ \emph{A
  Parallel Matrix-based Method for Computing Approximations in
  Incomplete Information Systems.}\\ Accepted for publication in the
  IEEE Transactions on Knowledge and Data Engineering
  (\href{http://www.computer.org/portal/web/tkde}{\textbf{TKDE}}).
\item
  \textbf{Junbo Zhang}, Tianrui Li, Yi Pan, Chuan Luo, Fei Teng.\\
  \emph{A Parallel and Incremental Algorithm for Updating Knowledge
  Based on Rough Sets in Cloud Computing Platform}.\\ Accepted for
  publication in \href{http://www.jos.org.cn/ch/index.aspx}{Journal of
  Software}. (in Chinese)
\item
  \textbf{Junbo Zhang}, Jian-Syuan Wong, Tianrui Li, Yi Pan,\\
  \href{http://dx.doi.org/10.1016/j.ijar.2013.08.003}{\emph{A Comparison
  of Parallel Large-scale Knowledge Acquisition Using Rough Set Theory
  on Different MapReduce Runtime Systems.}}\\
  \href{http://www.journals.elsevier.com/international-journal-of-approximate-reasoning}{\textbf{International
  Journal of Approximate Reasoning}}, vol.~55, no. 3, pp.~896-907, 2014.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Hongmei Chen,\\
  \href{http://dx.doi.org/10.1016/j.ins.2013.08.016}{\emph{Composite
  Rough Sets for Dynamic Data Mining.}}\\
  \href{http://www.journals.elsevier.com/information-sciences}{\textbf{Information
  Sciences}}, vol.~257, pp.~81-100, 2014.
\item
  \textbf{Junbo Zhang}, Dong Xiang, Tianrui Li, Yi Pan,\\
  \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?tp=\&arnumber=6449402\&contentType=Journals+\%26+Magazines\&queryText\%3DM2M\%3A+A+simple+Matlab-to-MapReduce+translator+for+Cloud+Computing}{\emph{M2M:
  A Simple Matlab-to-MapReduce Translator for Cloud Computing.}}\\
  \href{http://qhxb.lib.tsinghua.edu.cn/english/}{\textbf{Tsinghua
  Science and Technology}}, vol 18, no. 1, pp.~1-9, 2013.
\item
  Yi Pan, \textbf{Junbo Zhang},\\
  \href{http://www.ftrai.org/xe/index.php?mid=joc_published\&category=37964\&search_keyword=section\&search_target=title\&document_srl=38459}{\emph{Parallel
  Programming on Cloud Computing Platforms: Challenges and
  Solutions.}}\\ \href{http://www.ftrai.org/joc/}{\textbf{KITCS/FTRA
  Journal of Convergence}}, vol.~3, no. 4, pp.~23-28,2012.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Da Ruan, Zizhe Gao, Chengbing
  Zhao,\\ \href{http://dx.doi.org/10.1016/j.ins.2011.12.036}{\emph{A
  Parallel Method for Computing Rough Set Approximations.}}\\
  \href{http://www.journals.elsevier.com/information-sciences}{\textbf{Information
  Sciences}}, vol.~194, pp.~209-223, 2012.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Da Ruan, Dun Liu,\\
  \href{http://dx.doi.org/10.1016/j.ijar.2012.01.001}{\emph{Rough Sets
  Based Matrix Approaches with Dynamic Attribute Variation in Set-valued
  Information Systems.}}\\
  \href{http://www.journals.elsevier.com/international-journal-of-approximate-reasoning}{\textbf{International
  Journal of Approximate Reasoning}}, vol.~53, no. 4, pp.~620-635, 2012.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Da Ruan, Dun Liu,\\
  \href{http://dx.doi.org/10.1002/int.21523}{\emph{Neighborhood Rough
  Sets for Dynamic Data Mining.}}\\
  \href{http://onlinelibrary.wiley.com/journal/10.1002/{[}ISSN{]}1098-111X}{\textbf{International
  Journal of Intelligent Systems}}, vol.~27, no. 4, pp.~317-342, 2012.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Yi Pan.\\ \href{}{\emph{PLAR:
  Parallel Large-scale Attribute Reduction on Cloud Systems.}}\\ The
  14th International Conference on Parallel and Distributed Computing,
  Applications and Technologies
  (\href{http://pdcat13.csie.ntust.edu.tw/}{PDCAT}), Taipei, 2013.
\item
  \textbf{Junbo Zhang}, Chizheng Wang, Yi Pan, Tianrui Li.\\
  \href{}{\emph{Parallel Approaches to Neighborhood Rough Sets:
  Classification and Feature Selection.}}\\
  \href{http://kjb.szu.edu.cn/iske/}{The 8th International Conference on
  Intelligent Systems and Knowledge Engineering (ISKE)}, Shenzhen,
  China, 2013.
\item
  \textbf{Junbo Zhang}, Yun Zhu, Yi Pan, Tianrui Li.\\ \href{}{\emph{A
  Parallel Implementation of Computing Composite Rough Set
  Approximations on GPUs.}}\\ \href{http://cs.smu.ca/jrs2013/}{The
  Eighth International Conference on Rough Sets and Knowledge Technology
  (RSKT)}, Halifax, Canada, pp. 240-250, 2013.
\item
  \textbf{Junbo Zhang}, Jian-Syuan Wong, Tianrui Li, Yi Pan.\\
  \href{http://dx.doi.org/10.1109/ISBAST.2013.32}{\emph{H2T: A Simple
  Hadoop-to-Twister Translator for Cloud Computing.}}\\ 2013
  International Symposium on Biometrics and Security Technologies
  (ISBAST)\emph{,} Chengdu, China, pp.~180-186, 2013.
\item
  Hongmei Chen, Tianrui Li, \textbf{Junbo Zhang}, Chuan Luo.\\
  \emph{Probabilistic Composite Rough Set and Attribute Reduction.}\\
  The 7th International Conference on Intelligent Systems and Knowledge
  Engineering (ISKE), Beijing, China, 2012.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Hongmei Chen.\\
  \href{http://www.springerlink.com/content/g621611026534074/?MUD=MP}{\emph{Composite
  Rough Sets.}}\\ Proceedings of the 4th International Conference on
  Artificial Intelligence and Computational Intelligence (AICI),
  Chengdu, China, pp.~150-159, 2012.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Yi Pan.\\
  \href{http://doi.acm.org/10.1145/2351316.2351320}{\emph{Parallel Rough
  Set Based Knowledge Acquisition Using MapReduce from Big Data.}}\\
  \href{http://kdd2012.sigkdd.org/workshops.shtml}{ACM SIGKDD 2012
  Workshop on Big Data Mining (BigMine)}, Beijing, China,
  pp.~20-27,2012.
\item
  Anping Zeng, Tianrui Li, \textbf{Junbo Zhang}, Dun Liu.\\
  \href{http://dx.doi.org/10.1007/978-3-642-32115-3_4}{\emph{An
  Incremental Approach for Updating Approximations of Rough Fuzzy Sets
  under the Variation of the Object Sets.}}\\ Proceedings of the 8th
  International Conference on Rough Sets and Current Trends in Computing
  (\href{http://www.informatik.uni-trier.de/~ley/db/conf/rsctc/index.html}{RSCTC}),
  Chengdu, China, pp.~36-45 2012.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Yan Yang, Wei Wang.\\
  \href{http://dx.doi.org/10.1007/978-3-642-24425-4_23}{\emph{Neighborhood
  Rough Sets Based Matrix Approach for Calculation of the
  Approximations.}}\\ Proceedings of the 6th International Conference on
  Rough Sets and Knowledge Technology
  (\href{http://rskt.cs.uregina.ca}{RSKT}), Banff, Canada, pp.~166-171,
  2011.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Da Ruan.\\
  \href{http://dx.doi.org/10.1007/978-3-642-24806-1_11}{\emph{Rough Sets
  Based Incremental Rule Acquisition in Set-valued Information
  Systems.}}\\
  \href{http://www.fernuni-hagen.de/kn/phdseminar11/index_en.html}{Autonomous
  Systems: Developments and Trends}, Mallorca, Spain, vol.~391,
  pp.~135-146, 2012.
\item
  Zizhe Gao, Tianrui Li,\textbf{Junbo Zhang}, Chengbing Zhao, Zhonggang
  Wang.\\ \href{http://dx.doi.org/10.1007/978-3-642-25658-5_8}{\emph{A
  Parallel Method for Unpacking Original High Speed Rail Data Based on
  MapReduce.}}\\ Proceedings of the 6th International Conference on
  Intelligent Systems and Knowledge Engineering (ISKE), Shanghai, China,
  vol.~124, pp.~59-68, 2011.
\item
  \textbf{Junbo Zhang},Tianrui Li, Lei Wang.\\
  \href{http://dx.doi.org/10.1109/ISKE.2010.5680797}{\emph{A New Method
  for Calculation of the Approximations Under the Probabilistic Rough
  Sets.}}\\ Proceedings of 2010 IEEE International Conference on
  Intelligent Systems and Knowledge Engineering
  (\href{http://ieeexplore.ieee.org/xpl/mostRecentIssue.jsp?punumber=5676709}{ISKE}),
  Hangzhou, China, pp.~73-76, 2010.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Dun Liu.\\
  \href{http://dx.doi.org/10.1109/ISKE.2010.5680798}{\emph{An Approach
  for Incremental Updating Approximations in Variable Precision Rough
  Sets While Attribute Generalized.}}\\ Proceedings of 2010 IEEE
  International Conference on Intelligent Systems and Knowledge
  Engineering
  (\href{http://ieeexplore.ieee.org/xpl/mostRecentIssue.jsp?punumber=5676709}{ISKE}),
  Hangzhou, China, pp.~77-81, 2010.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Muhammad Zia ur Rehman, Shaoyong
  Li.\\ \href{http://dx.doi.org/10.1142/9789814324700_0116}{An Approach
  for Selection of the Proper Lever of Granularity in Granular
  Computing}. Proceedings of the 9th International FLINS Conference on
  Foundations and Applications of Computational Intelligence
  (\href{http://www.wikicfp.com/cfp/servlet/event.showcfp?eventid=7359\&copyownerid=2}{FLINS}),
  Chengdu, China, pp.~764-769, 2010.
\item
  Dun Liu, \textbf{Junbo Zhang}, Tianrui Li.\\
  \href{http://dx.doi.org/10.1142/9789814324700_0109}{\emph{A
  Probabilistic Rough Set Approach for Incremental Learning Knowledge on
  the Change of Attributes.}}\\ Proceedings of the 9th International
  FLINS Conference on Foundations and Applications of Computational
  Intelligence
  (\href{http://www.wikicfp.com/cfp/servlet/event.showcfp?eventid=7359\&copyownerid=2}{FLINS}),
  Chengdu, China, pp.~722-727, 2010.
\item
  Hongmei Chen, Tianrui Li, \textbf{Junbo Zhang}.\\
  \href{http://dx.doi.org/10.1109/GrC.2010.116}{\emph{A Method for
  Incremental Updating Approximations when Objects and Attributes Vary
  with Time.}}\\ Proceedings of 2010 IEEE International Conference on
  Granular Computing
  (\href{http://xanadu.cs.sjsu.edu/~grc/grc2010}{GrC}), California, USA,
  pp.~90-95, 2010.
\item
  Hongmei Chen, Tianrui Li,\textbf{Junbo Zhang}.\\
  \href{http://dx.doi.org/10.1109/GrC.2010.115}{\emph{A Method for
  Incremental Updating Approximations based on Variable Precision
  Set-valued Ordered Information Systems.}}\\ Proceedings of 2010 IEEE
  International Conference on Granular Computing
  (\href{http://xanadu.cs.sjsu.edu/~grc/grc2010}{GrC}), California, USA,
  pp.~96-101, 2010.
\item
  Shaoyong Li, Tianrui Li, \textbf{Junbo Zhang}.\\
  \href{http://dx.doi.org/10.1109/ISKE.2010.5680788}{\emph{Approach for
  Dynamically Updating Set Approximations Based Rough Sets While
  Condition Attributes Value Coarsening and Refining.}}\\ Proceedings of
  2010 IEEE International Conference on Intelligent Systems and
  Knowledge Engineering
  (\href{http://ieeexplore.ieee.org/xpl/mostRecentIssue.jsp?punumber=5676709}{ISKE}),
  Hangzhou, China, pp.~27-32, 2010.
\item
  Shaoyong Li, Tianrui Li, \textbf{Junbo Zhang}.\\
  \href{http://www.atlantis-press.com/php/paper-details.php?id=2011}{\emph{Updating
  Approximations Dynamically in Dominance-based Rough Sets.}}\\
  Proceedings of the International Conference on E-Business Intelligence
  (\href{http://cnais.sem.tsinghua.edu.cn/icebi2010}{ICEBI}), Kunming,
  China, pp.~534-540, 2010.
\item
  Dun Liu, Tianrui Li, \textbf{Junbo Zhang}.\\
  \href{http://www.atlantis-press.com/php/paper-details.php?id=2070}{\emph{An
  Incremental Approach for Rule Induction under Coarsening and Refining
  of Attribute Values in E-Business Systems.}}\\ Proceedings of the
  International Conference on E-Business Intelligence
  (\href{http://cnais.sem.tsinghua.edu.cn/icebi2010}{ICEBI}), Kunming,
  China, pp.~541-547, 2010.
\end{itemize}

\subsection{Awards \& Honors}\label{awards-honors}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  National Scholarship, China, 2013.
\item
  National Scholarship, China, 2012.
\item
  ``\href{http://baike.baidu.com/view/644025.htm}{Si Shi Yang Hua}`'
  Medal in \href{http://www.swjtu.edu.cn/}{Southwest Jiaotong
  University}, 2012. (Top 1/1000, the students' top honor of Southwest
  Jiaotong University).
\item
  2009-2014 Special Grade Scholarship for PhD Students,
  \href{http://www.swjtu.edu.cn/}{Southwest Jiaotong University}.
\item
  First Prize in the 9th ``Huawei Cup'' National Postgraduate
  Mathematical Contest in Modeling, China, 2012.
\item
  Second Prize in the 8th National Postgraduate Mathematical contest in
  Modeling, China, 2011.
\item
  Second Prize in the 2nd ``Huawei Cup'' Innovation Programming Contest,
  China, 2010.
\item
  Second Prize in the 6th National Postgraduate Mathematical contest in
  Modeling, China, 2009.
\item
  Second Prize in the 2nd Sichuan Provincial Programming Contest, China,
  2008.
\item
  Honorable Mention in the 33th ACM Asia Programming Contest, 2008.
\item
  Second Prize in the 1st Sichuan Provincial Programming Contest, China,
  2007.
\item
  Second Prize (the 12th Place in person) in the TopCoder Sichuan
  Provincial Contest, China, 2007.
\item
  Third Prize in National Electrical Engineering Association
  Mathematical Contest in Modeling, China, 2007.\\
\item
  The President Scholarship of School of Information Science and
  Technology, Southwest Jiaotong University, 2006, 2007.\\
\item
  2005-2009 Undergraduate Comprehensive Scholarship of Southwest
  Jiaotong University.
\end{itemize}

\subsection{Projects}\label{projects}

\begin{itemize}
\item
  {[}Nov. 2012 - Nov. 2013{]} Research on dynamic knowledge discovery
  techniques and efficient algorithms under granular computing, the
  Fostering Foundation for the Excellent Ph.D.~Dissertation of Southwest
  Jiaotong University, China. Leader and principal investigator.
\item
  {[}Otc. 2012 - Otc. 2013{]} Dynamic knowledge discovery system based
  on rough sets in cloud computing environments, the Science and
  Technology Planning Project of Sichuan Province, China. Leader and
  principal investigator.
\item
  {[}Otc. 2011 - Sep.2012{]}Research on dynamic knowledge discovery
  techniques under granular computing and probabilistic rough sets, and
  its fast algorithms based on cloud computing, the Doctoral Innovation
  Funding Project of Southwest Jiaotong University, China. Leader and
  principal investigator.
\item
  {[}Otc. 2011 - Sep.2012{]} Research on dynamic knowledge discovery
  system based on cloud computing and rough sets, the Young Software
  Innovation Foundation of Sichuan Province, China. Leader and principal
  investigator.
\item
  {[}May. 2012 - July.2012{]} 8-week NSF REU Undergraduate Summer
  Research Program hosted by the Department of Computer Science, Georgia
  State University, the National Science Foundation, USA. Participated
  as a mentor.
\item
  {[}Jan. 2012 - Present{]} Research on dynamic updating knowledge
  theories and algorithms based on granular computing, the National
  Natural Science Foundation of China.
\item
  {[}Jan. 2012 - Present{]} Research on composite rough set models and
  algorithms of knowledge discovery, the National Natural Science
  Foundation of China.
\item
  {[}Jan. 2009 - Dec. 2011{]} Research on incremental learning theories
  and methods based on granular computing, the National Natural Science
  Foundation of China.
\end{itemize}

\subsection{Professional Activities}\label{professional-activities}

\subsubsection{Review for Journal}\label{review-for-journal}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{http://tkdd.acm.org/}{ACM Transactions on Knowledge Discovery
  from Data (TKDD)}
\item
  \href{http://www.computer.org/portal/web/tc}{IEEE Transactions on
  Computers (TOC)}
\item
  \href{http://www.computer.org/portal/web/tcbb}{IEEE/ACM Transactions
  on Computational Biology and Bioinformatics (TCBB)}
\item
  \href{http://ieeexplore.ieee.org/xpl/RecentIssue.jsp?punumber=7728}{IEEE
  Transactions on NanoBioscience}
\item
  \href{http://www.editorialmanager.com/wwwj/}{World Wide Web Journal
  (WWWJ)}
\item
  \href{http://www.inderscience.com/jhome.php?jcode=ijcc}{International
  Journal of Cloud Computing (IJCC)}
\item
  \href{http://www.inderscience.com/jhome.php?jcode=ijbra}{International
  Journal of Bioinformatics Research and Applications (IJBRA)}
\item
  \href{http://www.atlantis-press.com/publications/ijcis/}{International
  Journal of Computational Intelligence Systems (IJCIS)}
\end{itemize}

\subsubsection{Extracurricular
Activities}\label{extracurricular-activities}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  IBM Cloud Academy CON, NC, Research Triangle Park (RTP), North
  Carolina, USA, Apr. 2012.
\item
  2010 Workshop on Frontiers of Data Management, Soochow University,
  Suzhou, China, Dec. 2010.
\item
  2010 Workshop on Massive Data Mining and Knowledge Discovery,
  Southwest Jiaotong University, Chengdu, China, Nov. 2010.
\item
  2010 China Computer Federation Advanced Disciplines Lectures (the 11th
  issue) - Massive Data Mining and Knowledge Discovery, Southwest
  Jiaotong University, Chengdu, China, Nov. 2010.
\item
  Intel Software College - Multi-core Programming for Academia, Fudan
  University, Shanghai, China, 2010.
\item
  2010 National Graduate Summer School - Data Intensive Computing and
  Unstructured Data Management, Renmin University of China, Beijing,
  China, Jul. 2010.
\item
  2009 Workshop on Massive Data Mining and Knowledge Discovery,
  Southwest Jiaotong University, Chengdu, China, Dec. 2009.
\item
  National Graduate Summer School (Dragon Star Plan) - Data Mining,
  Zhejiang University, Hangzhou, China, 2009.
\end{itemize}

\subsection{Skills}\label{skills}

\begin{description}
\item[Operating System]
Linux-based OS, Mac OS, Windows XP, Windows 7/8
\item[Programming Language]
C, C++, Python, Java, Shell, Matlab (and various) languages with
practical experiences.
\item[Others]
Hadoop, Weka, LaTex, MS Office(Visio, Word, Excel, PowerPoint)
\end{description}

\end{document}

