%\documentclass[]{article}
\documentclass[10pt,a4paper]{article}

%% Added By Lucktroy
\usepackage{booktabs}
\usepackage{mdwlist}
\renewenvironment{description}{
  \begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{8em}}
}{
  \end{basedescript}
}
%%

\usepackage{geometry} 		% 設定邊界
\geometry{
  top=1in,
  inner=1in,
  outer=1in,
  bottom=1in,
  headheight=3ex,
  headsep=2ex
}
\usepackage{tgpagella} % Use the TeX Gyre Pagella font throughout the document
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec} 	% 允許設定字體
  \usepackage{xeCJK} 		% 分開設置中英文字型
  \setCJKmainfont{Adobe Kaiti Std} 	% 設定中文字型
  %\setmainfont{Georgia} 	% 設定英文字型
  %\setromanfont{Georgia} 	% 字型
  %\setmonofont{Courier New}
  %\linespread{1.2}\selectfont 	% 行距
  %\XeTeXlinebreaklocale "zh" 	% 針對中文自動換行
  %\XeTeXlinebreakskip = 0pt plus 1pt % 字與字之間加入0pt至1pt的間距，確保左右對整齊
  %\parindent 0em 		% 段落縮進
  %\setlength{\parskip}{20pt} 	% 段落之間的距離
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines

\title{\huge 在OSX平台上的XeLaTeX中文測試} % 設置標題，使用巨大字體
\author{FoolEgg.com} 		% 設置作者
\date{February 2013} 		% 設置日期
\usepackage{titling}
\setlength{\droptitle}{-8em} 	% 將標題移動至頁面的上面

\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancyplain}

\setcounter{secnumdepth}{0}

\author{}
\date{}

\begin{document}

\section{\texttt{Junbo Zhang}}\label{section}

\subsection{Publications}\label{publications}

\small

\paragraph{Journal Papers}\label{journal-papers}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Junbo Zhang}, Yun Zhu, Yi Pan, Tianrui Li.\\
  \href{}{\emph{Efficient Parallel Boolean Matrix Based Algorithms for
  Computing Composite Rough Set Approximations.}}\\
  \href{http://www.journals.elsevier.com/information-sciences}{\textbf{Information
  Sciences}}, accept, 2015.
\item
  \textbf{Junbo Zhang}, Jian-Syuan Wong, Yi Pan, Tianrui Li.\\
  \href{http://dx.doi.org/10.1109/TKDE.2014.2330821}{\emph{A Parallel
  Matrix-based Method for Computing Approximations in Incomplete
  Information Systems.}}\\ IEEE Transactions on Knowledge and Data
  Engineering
  (\href{http://www.computer.org/portal/web/tkde}{\textbf{TKDE}}), 2015.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Yi Pan, Chuan Luo, Fei Teng.\\
  \href{http://dx.doi.org/10.13328/j.cnki.jos.004590}{\emph{A Parallel
  and Incremental Algorithm for Updating Knowledge Based on Rough Sets
  in Cloud Computing Platform.}}\\ Accepted for publication in
  \href{http://www.jos.org.cn/ch/index.aspx}{\textbf{Journal of
  Software}}. (in Chinese)
\item
  \textbf{Junbo Zhang}, Jian-Syuan Wong, Tianrui Li, Yi Pan.\\
  \href{http://dx.doi.org/10.1016/j.ijar.2013.08.003}{\emph{A Comparison
  of Parallel Large-scale Knowledge Acquisition Using Rough Set Theory
  on Different MapReduce Runtime Systems.}}\\
  \href{http://www.journals.elsevier.com/international-journal-of-approximate-reasoning}{\textbf{International
  Journal of Approximate Reasoning}}, vol.~55, no. 3, pp.~896-907, 2014.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Hongmei Chen.\\
  \href{http://dx.doi.org/10.1016/j.ins.2013.08.016}{\emph{Composite
  Rough Sets for Dynamic Data Mining.}}\\
  \href{http://www.journals.elsevier.com/information-sciences}{\textbf{Information
  Sciences}}, vol.~257, pp.~81-100, 2014.
\item
  \textbf{Junbo Zhang}, Dong Xiang, Tianrui Li, Yi Pan.\\
  \href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?tp=\&arnumber=6449402\&contentType=Journals+\%26+Magazines\&queryText\%3DM2M\%3A+A+simple+Matlab-to-MapReduce+translator+for+Cloud+Computing}{\emph{M2M:
  A Simple Matlab-to-MapReduce Translator for Cloud Computing.}}\\
  \href{http://qhxb.lib.tsinghua.edu.cn/english/}{\textbf{Tsinghua
  Science and Technology}}, vol 18, no. 1, pp.~1-9, 2013.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Da Ruan, Zizhe Gao, Chengbing
  Zhao.\\ \href{http://dx.doi.org/10.1016/j.ins.2011.12.036}{\emph{A
  Parallel Method for Computing Rough Set Approximations.}}\\
  \href{http://www.journals.elsevier.com/information-sciences}{\textbf{Information
  Sciences}}, vol.~194, pp.~209-223, 2012.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Da Ruan, Dun Liu.\\
  \href{http://dx.doi.org/10.1016/j.ijar.2012.01.001}{\emph{Rough Sets
  Based Matrix Approaches with Dynamic Attribute Variation in Set-valued
  Information Systems.}}\\
  \href{http://www.journals.elsevier.com/international-journal-of-approximate-reasoning}{\textbf{International
  Journal of Approximate Reasoning}}, vol.~53, no. 4, pp.~620-635, 2012.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Da Ruan, Dun Liu.\\
  \href{http://dx.doi.org/10.1002/int.21523}{\emph{Neighborhood Rough
  Sets for Dynamic Data Mining.}}\\
  \href{http://onlinelibrary.wiley.com/journal/10.1002/{[}ISSN{]}1098-111X}{\textbf{International
  Journal of Intelligent Systems}}, vol.~27, no. 4, pp.~317-342, 2012.
\end{enumerate}

\subsubsection{Conference Papers}\label{conference-papers}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Junbo Zhang}, Guangjian Tian, Yadong Mu, Wei Fan.\\
  \href{http://dx.doi.org/10.1145/2623330.2623618}{\emph{Supervised Deep
  Learning with Auxiliary Networks.}}\\ Proceedings of the 20th ACM
  SIGKDD Conference on Knowledge Discovery and Data Mining
  (\href{http://www.kdd.org/kdd2014/}{\textbf{KDD 2014}}), New York,
  USA, 2014, pp.~353-361.\\ (AR: 151/1036 = 14.6\%)
\item
  \textbf{Junbo Zhang}, Tianrui Li, Yi Pan.\\
  \href{http://dx.doi.org/10.1109/PDCAT.2013.36}{\emph{PLAR: Parallel
  Large-scale Attribute Reduction on Cloud Systems.}}\\ The 14th
  International Conference on Parallel and Distributed Computing,
  Applications and Technologies
  (\href{http://pdcat13.csie.ntust.edu.tw/}{\textbf{PDCAT 2013}}),
  Taipei, 2013, pp.~184-191.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Yi Pan.\\
  \href{http://doi.acm.org/10.1145/2351316.2351320}{\emph{Parallel Rough
  Set Based Knowledge Acquisition Using MapReduce from Big Data.}}\\ ACM
  SIGKDD 2012 Workshop on Big Data Mining
  (\href{http://kdd2012.sigkdd.org/workshops.shtml}{\textbf{BigMine
  2012}}), Beijing, China, pp.~20-27,2012.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Yi Pan.\\ \href{}{\emph{PLAR:
  Parallel Large-scale Attribute Reduction on Cloud Systems.}}\\ The
  14th International Conference on Parallel and Distributed Computing,
  Applications and Technologies
  (\href{http://pdcat13.csie.ntust.edu.tw/}{PDCAT}), Taipei, 2013.
\item
  \textbf{Junbo Zhang}, Yun Zhu, Yi Pan, Tianrui Li.\\ \href{}{\emph{A
  Parallel Implementation of Computing Composite Rough Set
  Approximations on GPUs.}}\\ \href{http://cs.smu.ca/jrs2013/}{The
  Eighth International Conference on Rough Sets and Knowledge Technology
  (RSKT)}, Halifax, Canada, pp. 240-250, 2013.
\item
  \textbf{Junbo Zhang}, Jian-Syuan Wong, Tianrui Li, Yi Pan.\\
  \href{http://dx.doi.org/10.1109/ISBAST.2013.32}{\emph{H2T: A Simple
  Hadoop-to-Twister Translator for Cloud Computing.}}\\ 2013
  International Symposium on Biometrics and Security Technologies
  (ISBAST)\emph{,} Chengdu, China, pp.~180-186, 2013.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Hongmei Chen.\\
  \href{http://www.springerlink.com/content/g621611026534074/?MUD=MP}{\emph{Composite
  Rough Sets.}}\\ Proceedings of the 4th International Conference on
  Artificial Intelligence and Computational Intelligence (AICI),
  Chengdu, China, pp.~150-159, 2012.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Yan Yang, Wei Wang.\\
  \href{http://dx.doi.org/10.1007/978-3-642-24425-4_23}{\emph{Neighborhood
  Rough Sets Based Matrix Approach for Calculation of the
  Approximations.}}\\ Proceedings of the 6th International Conference on
  Rough Sets and Knowledge Technology
  (\href{http://rskt.cs.uregina.ca}{RSKT}), Banff, Canada, pp.~166-171,
  2011.
\item
  \textbf{Junbo Zhang},Tianrui Li, Lei Wang.\\
  \href{http://dx.doi.org/10.1109/ISKE.2010.5680797}{\emph{A New Method
  for Calculation of the Approximations Under the Probabilistic Rough
  Sets.}}\\ Proceedings of 2010 IEEE International Conference on
  Intelligent Systems and Knowledge Engineering
  (\href{http://ieeexplore.ieee.org/xpl/mostRecentIssue.jsp?punumber=5676709}{ISKE}),
  Hangzhou, China, pp.~73-76, 2010.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Dun Liu.\\
  \href{http://dx.doi.org/10.1109/ISKE.2010.5680798}{\emph{An Approach
  for Incremental Updating Approximations in Variable Precision Rough
  Sets While Attribute Generalized.}}\\ Proceedings of 2010 IEEE
  International Conference on Intelligent Systems and Knowledge
  Engineering
  (\href{http://ieeexplore.ieee.org/xpl/mostRecentIssue.jsp?punumber=5676709}{ISKE}),
  Hangzhou, China, pp.~77-81, 2010.
\item
  \textbf{Junbo Zhang}, Tianrui Li, Muhammad Zia ur Rehman, Shaoyong
  Li.\\ \href{http://dx.doi.org/10.1142/9789814324700_0116}{An Approach
  for Selection of the Proper Lever of Granularity in Granular
  Computing}. Proceedings of the 9th International FLINS Conference on
  Foundations and Applications of Computational Intelligence
  (\href{http://www.wikicfp.com/cfp/servlet/event.showcfp?eventid=7359\&copyownerid=2}{FLINS}),
  Chengdu, China, pp.~764-769, 2010.
\end{enumerate}

\paragraph{Book Chapter}\label{book-chapter}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{Junbo Zhang}, Tianrui Li, Da Ruan.\\
  \href{http://dx.doi.org/10.1007/978-3-642-24806-1_11}{\emph{Rough Sets
  Based Incremental Rule Acquisition in Set-Valued Information
  Systems.}}\\
  \href{http://www.springer.com/engineering/computational+intelligence+and+complexity/book/978-3-642-24805-4}{\textbf{Autonomous
  Systems: Developments and Trends}}, pp.~135-146, 2012.
\end{enumerate}

\subsection{Awards \& Honors}\label{awards-honors}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  National Scholarship, China, 2013.
\item
  National Scholarship, China, 2012.
\item
  ``\href{http://baike.baidu.com/view/644025.htm}{Si Shi Yang Hua}''
  Medal in \href{http://www.swjtu.edu.cn/}{Southwest Jiaotong
  University}, 2012. (Top 1/1000, the students' top honor of Southwest
  Jiaotong University).
\item
  2009-2014 Special Grade Scholarship for PhD Students,
  \href{http://www.swjtu.edu.cn/}{Southwest Jiaotong University}.
\item
  First Prize in the 9th ``Huawei Cup'' National Postgraduate
  Mathematical Contest in Modeling, China, 2012.
\item
  Second Prize in the 8th National Postgraduate Mathematical contest in
  Modeling, China, 2011.
\item
  Second Prize in the 2nd ``Huawei Cup'' Innovation Programming Contest,
  China, 2010.
\item
  Second Prize in the 6th National Postgraduate Mathematical contest in
  Modeling, China, 2009.
\item
  Second Prize in the 2nd Sichuan Provincial Programming Contest, China,
  2008.
\item
  Honorable Mention in the 33th ACM Asia Programming Contest, 2008.
\item
  Second Prize in the 1st Sichuan Provincial Programming Contest, China,
  2007.
\item
  Second Prize (the 12th Place in person) in the TopCoder Sichuan
  Provincial Contest, China, 2007.
\item
  Third Prize in National Electrical Engineering Association
  Mathematical Contest in Modeling, China, 2007.
\item
  The President Scholarship of School of Information Science and
  Technology, Southwest Jiaotong University, 2006, 2007.
\item
  2005-2009 Undergraduate Scholarship of Southwest Jiaotong University,
  China.
\end{itemize}

\end{document}

